Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-01 doc/main_jfm.tex
starting to work through Sec 4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
Janus-vesicle undergoes tank-treading in a shear flow and vertical
migration in a Poiseuille flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting Janus-vesicles with a continuum model of a pair of vesicles.

@@

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{validation} we validate our model, and in \S~\ref{results} we
present simulation results for a single and pair of Janus-vesicles under
various flowing conditions. Finally we provide discussion and outlook
for future directions in \S~\ref{conclusion}.

@@

\subsection{Model Parameters}
To extract physical quantities of the target structure, 
we select particles that are disks with diameter 
$l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
$\xx - \aa_i$ and $\dd_i$,  where the vectors $\aa_i$ and $\dd_i$ are the particle centre and director respectively. 
This makes it so that the director points in the direction of the hydrophobic side of the JP. 
The other physical parameters are 
%\begin{equation}
%\label{eq:parameters}
decay length $\rho = 2 l_0$, 
repulsion length $\rho_0 = 0.2l_0$, 
repulsion strength is $M=4.0$~$k_BT$, 
interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, 
and $\mu = \text{1 cP} = \text{1 pN ns nm}^{-2}$ for the viscosity of water at room temperature.  
\cite{Fu20} have provide physical quantities static JP bilayers.%\end{equation}

We consider the behavior of JP vesicles under various external flows.
To do so, we nondimensionalize the problem through the change of variables 
%\begin{equation}
%\label{eq:nondimensionalize}
$t \mapsto t \text{ ns},$ % \quad
$\xx \mapsto \xx \text{ nm}$, %\quad 
$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
 $p \mapsto p \text{ pN nm}^{-2}$.
%\end{equation}
For the remainder of the manuscript, the time axes are for ns; the pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$
are for pN nm$^{-2}$. Finally, the
dimensionless shear rate is $\chi = \dot\gamma \tau$ for the dimensional shear rate  $\dot\gamma$
in ns$^{-1}$ and characteristic time $\tau = 1$ ns. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.

\subsection{Self-Assembly and Relaxation}
\begin{figure}
\centering
\includegraphics[height=2in]{relax2.eps}
\includegraphics[height=2in]{relax.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(black) and $t=1000$(red) with particle directors.
  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines. In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer. After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
  }
    \label{figure2}
\end{figure}

In order to examine the hydrodynamics interactions of JP vesicles, 
it is necessary to have a suitable, initial, equilibrium vesicle. 
This is ensures that the dynamics of the bilayer under a shear flow, for example, reach consistent outcomes.
For our target vesicle, we start with $N=58$ JP arranged in two circular, apposing monolayers 
of about $8$ length units. The directors of outer monolayer point inward and the directors of the inner monolayer point outward
(figure~\ref{figure2}a).
The JP of this chosen configuration are generally not in equilibrium.  Rather, the inter-particle distances and orientations 
must make slight adjustments so that attraction and repulsion are balance. 
Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity components 
${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of the particle orientation decrease exponentially with an approximation decaying rate $\sim0.005$. 
A local energy minimum and the equilibrium configuration is therefore rapidly attained.  
The equilibrium configuration in figure~\ref{figure2}a is slightly elliptical.  The equilibrium eccentricity vanishes for larger $N_b$ (figure~\ref{figure2}e).

@@

The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
In figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
and finally a configuration with 117 particles but with diameter 1.25 nm rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).
Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
(The values for $L_0$ are the asymptotic values for $L$ in figure \ref{figure:permeability}c).

Figure \ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see figure \ref{figure2}c,d),
$R = L/2\pi$ is the vesicle radius, and the horizontal axis is for the relative stretch. The solid lines are linear fits,
showing that for circular JP vesicles, $R\Delta P$ is basically proportional to relative stretching $L/L_0 - 1$ . The proportionality constant is the same 
for the 58 and 119 particle cases where the diameters are the same, suggesting that the stretching modulus $K_A$ of JP bilayers 
is independent of the number of particles. The 117 particle case had diameters 1.25 nm and this data set gave a smaller stretching modulus  $K_A = 102$ pN nm$^{-1}$.  The interpretation is that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$ fixed, lead to different physical properties.

Furthermore, figure \ref{figure:permeability}b and shows that $L\Delta P$ is proportional to $\frac{dA}{dt}$
in accord with \eqref{eq:perm}.  The slopes of the linear fits give the hydraulic permeability coefficient $P.$
The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$
for the 58 and 119 particle cases, respectively.  These values suggest that the JP bilayer permeability is independent 
of particle number, as was the case for the stretching modulus. 
The permeability for the 117 particle number case was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because 
hydrophobic attraction vanishes with particle size, leading to larger gaps between the particles for the same repulsion. 
The hydraulic permeability we calculate, however, is not in agreement with experimentally derived values and is larger by
a few orders of magnitude. This discrepancy is perhaps due to inter-particle distance of the JP being relatively large to the 
inter-molecular spacing of lipids in real bilayers.  In future studies, we can test this hypothesis be changing the repulsion strength and length 
for example.

Since the vesicles in figure \ref{figure2}a are nearly we circular, we can 
combine \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, to derive  
\begin{equation}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{equation}
The theoretical time courses for \eqref{eq:perm_solution} are in good quantitative agreement with the JP data 
for (figure \ref{figure:permeability}c).

@@

The centroid of the pre-relaxed $58$-body Janus vesicle is initially
placed at the origin and the shear flow with a certain shear rate $\chi$
is applied. Snapshots of the Janus-vesicle in a shear flow with a shear
rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
show the initial shape obtained from the relaxation run and the deformed
configurations of the Janus-vesicle at time $t=4000$ are in panels (c)
and (d). The background color in panels (a) and (c) is the strength of
the action of the hydrophobic attraction. Red corresponds to a strong
action while blue is weak action. The hydrophobic layer clearly has the
strongest action. To demonstrate the tank-treading behavior of the
vesicle, panels (b) and (d) provide the streamlines of the fluid
velocity around the Janus-vesicle. In panel (d), we can clearly observe
the clockwise tank-treading motion.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  Janus-vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed Janus-vesicle at
  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%

To extract additional physical properties of the proposed model, we
compute the total length, reduced area, and excess length of the bilayer
structure. The enclosed area and the total length of the structure are
calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
where $A$ the area, and $L$ the total length of the Janus-vesicle, and
the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Figure~\ref{figure4} shows these quantities for a Janus-vesicle
suspended in a shear flow with shear rates
$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
is nearly circular, the reduced area decreases from an initial value
close to $1$. The smooth curves in panel (a) are best fits of the
exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
decay rate $k$ is independent of the shear rate for sufficiently large
shear rates, and the terminal reduced areas of each case are shown in
the inset. We see that lower shear rates generate a higher final reduced
area. In particular, we observe that the reduce area converges
relatively early when the shear rate is lower than $\chi=0.003$. 
%and has a faster convergence than the high shear rate cases.
Panel (c) shows that the total arc length remains constant for all time
with all four shear rates. Combining the behavior of the reduced area
and the total arc length, the excess length must increase in time and be
larger for higher shear rates as observed in panel (d). In all these
results, there are oscillations that can be explained by the granularity
of the Janus-vesicle which results in a midplane that is non-smooth.
%Overall the total lengths of the bilayer have the same converging value
%in all test shear rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated Janus-vesicle allows us to consider inter-monolayer slip
between two leaflets. When the shear rate is sufficiently large, take
$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
pair of particles over time. The pair we consider are colored in blue
and yellow. In this series of tests, we compute the mean particle
position and mean angle $\theta(t)$ between the particle relative
positions with respect to the vesicle center. It is clear that the outer
leaflet has larger tangential velocity than the inner leaflet since the
mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
is consistent with what has been seen in articles in molecular dynamics
simulations.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the Janus-vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  at larger shear rates.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the
flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
The behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area,
the steady-state shape can be either an symmetric parachute or
an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009}.

%Besides the tests of a Janus-vesicle in a shear flow, an interesting
%test can also use the proposed model and the setup. Consider a
%symmetric parabolic flow about the $x$-axis,~\cite{Kaoui09} studied
%shapes of the red blood cell immersed in a parabolic flow using a
%continuum model. With a similar setup, the background flow for this set
%of simulations is given by

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the Janus-vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed Janus-vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction which decreases toward $y=1$ for a period of time and then
starts to have an oscillatory motion due to the granularity of the
Janus-vesicle.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A Janus-vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a Janus-vesicle suspended in
  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
  configuration is generated when $t=10000$. The inset plots the
  trajectory of mean $y$-position over the time.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a JP vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
JP vesicle undergoes tank-treading in a shear flow and vertical
migration in a Poiseuille flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

@@

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{results} we validate our model and present simulation results
for a single and pair of JP vesicles under various flowing conditions.
Finally we provide discussion and outlook for future directions in
\S~\ref{conclusion}.

@@

\subsection{Model Parameters}
To extract physical quantities of the target structure, we select
particles that are disks with diameter $l_0 = 2.5$ nm representing the
characteristic thickness of monolayers. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
and director respectively. With this choice, the director points in the
direction of the hydrophobic side of the JP. The other physical
parameters are the decay length $\rho = 2 l_0$, the repulsion length
$\rho_0 = 0.2l_0$, the repulsion strength is $M=4.0$~$k_BT$, the
interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, and $\mu
= \text{1 cP} = \text{1 pN ns nm}^{-2}$ is the viscosity of water at
room temperature. \cite{Fu20} provides physical quantities for static JP
bilayers.

We consider the behavior of JP vesicles under various external flows.
To do so, we nondimensionalize the problem through the change of
variables 
%\begin{equation}
%\label{eq:nondimensionalize}
$t \mapsto t \text{ ns},$ % \quad
$\xx \mapsto \xx \text{ nm}$, %\quad 
$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
$p \mapsto p \text{ pN nm}^{-2}$.
%\end{equation}
For the remainder of the manuscript, the time axes are in ns, and the
pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$ are
in pN nm$^{-2}$. Finally, the dimensionless shear rate is $\chi =
\dot\gamma \tau$ for the dimensional shear rate $\dot\gamma$ in
ns$^{-1}$ and the characteristic time is $\tau = 1$~ns. The time step
size $\Delta t=0.2$ is used for all simulations in this work including
the relaxation run.

\subsection{Self-Assembly and Relaxation}
\begin{figure}
\centering
\includegraphics[height=2in]{relax2.eps}
\includegraphics[height=2in]{relax.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

In order to examine the hydrodynamics interactions of JP vesicles, it is
necessary to have a suitable, initial, equilibrium vesicle.  This is
ensures that the dynamics of the bilayer under a shear flow, for
example, reach consistent outcomes.  For our target vesicle, we start
with $N=58$ JP arranged in two circular, apposing monolayers of about
$8$ length units. The directors of outer monolayer point inward and the
directors of the inner monolayer point outward (Figure~\ref{figure2}a).
The JP of this chosen configuration are generally not in equilibrium.
Rather, the inter-particle distances and orientations must make slight
adjustments so that attraction and repulsion are balance.
Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity
components ${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of
the particle orientation decrease exponentially with an approximation
decaying rate $\sim0.005$.  A local energy minimum and the equilibrium
configuration is therefore rapidly attained.  The equilibrium
configuration in Figure~\ref{figure2}a is slightly elliptical.  The
equilibrium eccentricity vanishes for larger $N_b$
(Figure~\ref{figure2}e).

@@

The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
In Figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
and finally a configuration with 117 particles but with diameter 1.25 nm rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).
Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
(The values for $L_0$ are the asymptotic values for $L$ in Figure \ref{figure:permeability}c).

Figure~\ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see Figure~\ref{figure2}c,d),
$R = L/2\pi$ is the vesicle radius, and the horizontal axis is for the relative stretch. The solid lines are linear fits,
showing that for circular JP vesicles, $R\Delta P$ is basically proportional to relative stretching $L/L_0 - 1$ . The proportionality constant is the same 
for the 58 and 119 particle cases where the diameters are the same, suggesting that the stretching modulus $K_A$ of JP bilayers 
is independent of the number of particles. The 117 particle case had diameters 1.25 nm and this data set gave a smaller stretching modulus  $K_A = 102$ pN nm$^{-1}$.  The interpretation is that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$ fixed, lead to different physical properties.

Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeability
coefficient $P.$ The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
particle cases, respectively.  These values suggest that the JP bilayer
permeability is independent of particle number, as was the case for the
stretching modulus.  The permeability for the 117 particle number case
was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because
hydrophobic attraction vanishes with particle size, leading to larger
gaps between the particles for the same repulsion.  The hydraulic
permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude. This discrepancy is perhaps due to inter-particle distance of
the JP being relatively large to the inter-molecular spacing of lipids
in real bilayers.  In future studies, we can test this hypothesis be
changing the repulsion strength and length for example.

Since the vesicles in Figure~\ref{figure2}a are nearly we circular, we
can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive  
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure:permeability}c).

@@

The centroid of the pre-relaxed $58$-body Janus vesicle is initially
placed at the origin and the shear flow with a certain shear rate $\chi$
is applied. Snapshots of the JP vesicle in a shear flow with a shear
rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
show the initial shape obtained from the relaxation run and the deformed
configurations of the JP vesicle at time $t=4000$ are in panels (c)
and (d). The background color in panels (a) and (c) is the strength of
the action of the hydrophobic attraction. Red corresponds to a strong
action while blue is weak action. The hydrophobic layer clearly has the
strongest action. To demonstrate the tank-treading behavior of the
vesicle, panels (b) and (d) provide the streamlines of the fluid
velocity around the JP vesicle. In panel (d), we can clearly observe
the clockwise tank-treading motion.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  JP vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed JP vesicle at
  $t=4000$. At this configuration the JP vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%

To extract additional physical properties of the proposed model, we
compute the total length, reduced area, and excess length of the bilayer
structure. The enclosed area and the total length of the structure are
calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
where $A$ the area, and $L$ the total length of the JP vesicle, and
the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Figure~\ref{figure4} shows these quantities for a JP vesicle
suspended in a shear flow with shear rates
$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
is nearly circular, the reduced area decreases from an initial value
close to $1$. The smooth curves in panel (a) are best fits of the
exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
decay rate $k$ is independent of the shear rate for sufficiently large
shear rates, and the terminal reduced areas of each case are shown in
the inset. We see that lower shear rates generate a higher final reduced
area. In particular, we observe that the reduce area converges
relatively early when the shear rate is lower than $\chi=0.003$. 
%and has a faster convergence than the high shear rate cases.
Panel (c) shows that the total arc length remains constant for all time
with all four shear rates. Combining the behavior of the reduced area
and the total arc length, the excess length must increase in time and be
larger for higher shear rates as observed in panel (d). In all these
results, there are oscillations that can be explained by the granularity
of the JP vesicle which results in a midplane that is non-smooth.
%Overall the total lengths of the bilayer have the same converging value
%in all test shear rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between two leaflets. When the shear rate is sufficiently large, take
$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
pair of particles over time. The pair we consider are colored in blue
and yellow. In this series of tests, we compute the mean particle
position and mean angle $\theta(t)$ between the particle relative
positions with respect to the vesicle center. It is clear that the outer
leaflet has larger tangential velocity than the inner leaflet since the
mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
is consistent with what has been seen in articles in molecular dynamics
simulations.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  at larger shear rates.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$.
The behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area,
the steady-state shape can be either an symmetric parachute or
an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009}.

%Besides the tests of a JP vesicle in a shear flow, an interesting
%test can also use the proposed model and the setup. Consider a
%symmetric parabolic flow about the $x$-axis,~\cite{Kaoui09} studied
%shapes of the red blood cell immersed in a parabolic flow using a
%continuum model. With a similar setup, the background flow for this set
%of simulations is given by

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed JP vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction which decreases toward $y=1$ for a period of time and then
starts to have an oscillatory motion due to the granularity of the
JP vesicle.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in
  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
  configuration is generated when $t=10000$. The inset plots the
  trajectory of mean $y$-position over the time.}
\end{figure}
